A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-19 doc/paper1-submission/paper5.tex
expanded legends to deal with our confusing omission of the trivial subproblems

\caption{Subproblems generated from the exemplified trees shown in figure \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__ab1c}

@@

\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{Figures__grafted_solution__grafted_solution_ottnames\lyxdot tre}
\par\end{centering}
\caption{Grafted solution produced from the subproblems from
figure \ref{fig:subproblem-solutions.} and which is the 
backbone onto which taxa that are not included in any phylogeny
will be placed.}
\label{fig:grafted-solution}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{Figures__labelled_supertree__labelled_supertree_only_taxon_names\lyxdot tre}
\par\end{centering}
\caption{Unpruned tree with internal taxa. Nodes E2, F2, and D have been re-added
to the tree. The nodes E and F are no longer monotypic.}
\end{figure}

>>>>

\caption{Subproblems generated from the exemplified trees shown in figure \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.
Similarly, the trivial problems that list E1 and F1 as the only daughters
of taxa E and F have been omitted.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__ab1c}

@@

\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{Figures__grafted_solution__grafted_solution_ottnames\lyxdot tre}
\par\end{centering}
\caption{Grafted solution produced from the subproblems from
figure \ref{fig:subproblem-solutions.} and which is the 
backbone onto which taxa that are not included in any phylogeny
will be placed.
In a real analysis, the tips shown as E and F here
would be monotypic taxa (with children E1 and F1, respectively)
from the trivial subproblems that were omitted from from figure \ref{fig:subproblems-example}.}
\label{fig:grafted-solution}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{Figures__labelled_supertree__labelled_supertree_only_taxon_names\lyxdot tre}
\par\end{centering}
\caption{Unpruned tree with internal taxa. Taxa unsampled in phylogenetic
statements have been added to the grafted tree shown
in figure \ref{fig:grafted-solution}.}
\end{figure}
